Towards a Pandemic-Scale Ancestral Recombination Graph of SARS-CoV-2

### 2023-04-21 paper.tex
Move code availability down and add data availability statement

\subsubsection{Code availability} The source code implementing the sc2ts
pipeline is available via GitHub
\url{https://github.com/jeromekelleher/sc2ts/}. The sc2ts pipeline uses various
functions and algorithms implemented in tskit and tsinfer
\url{https://github.com/tskit-dev/}. The pipeline uses the SciPy implementation
of the UPGMA algorithm to build daily trees
\url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.cluster.hierarchy.average.html}.
The Jupyter notebooks used to produce the results described herein are also
available on GitHub \url{https://github.com/jeromekelleher/sc2ts-paper/}.

@@

>>>>

@@

\section{Data Availability}
The source code for \texttt{sc2ts} is
is available on GitHub
\url{https://github.com/jeromekelleher/sc2ts/}.
The Jupyter notebooks and code used to produce the results described here are also
available on GitHub \url{https://github.com/jeromekelleher/sc2ts-paper/}.

% TODO what's the right way to say this?
The inferred ARGs described here are available on request to those with
the appropriate GISAID data access.
